Adaptive Approximation for Multivariate Linear Problems \\ with Inputs Lying in a Cone

### 2018-11-06 RICAM2018NovTalk.tex
trimming

\vspace{-9ex}
\uncover<2->{\alert{Solvability}\footfullcite{KunEtal19a}: $\ca(\cc) \ne \emptyset$

@@

\uncover<3->{\alert{Cost}: $\cost(\app,f,\varepsilon) = $ \# of function data
\newline
 $\cost(\app,\cc,\varepsilon, \rho) = \max_{f \in \cc \cap \cb_{\rho}} \cost(\app,f,\varepsilon)$
 \newline
 $\cb_{\rho} := \{f \in \cf : \norm[\cf]{f} \le \rho \}$

@@

\uncover<4->{\alert{Tractability}\footfullcite{NovWoz08a}: $\comp(\app,\cc,\varepsilon, \rho) \le C \rho^p\varepsilon^{-p} d^{q} $}

@@

    \item Union of \alert{cones} is a \alert{cone}

    \item Philosophy of our algorithms:  \alert{What we cannot observe is not much worse than what we can observe}

@@

\begin{frame}{Spaces of Inputs and Outputs}

We focus on Banach spaces that look like

\vspace{-5ex}
\begin{align*}
    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[r,\vlambda]{\hf} : = \norm[r]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \quad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
    \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[t]{\hg}\biggr \}, \qquad S(u_{\vj}) = v_{\vj}, \\
    \text{E.g., } & \text{ Function recovery: } S(u_{\vj}) = u_{\vj} = v_{\vj} \\
    & \text{ Integration: } S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx  = v_\vj\\
    \Sapp(f,n) &= \sum_{i=1}^n L_i(f) g_i = \sum_{\vj \in \cn} \hf(\vj) \Sapp(u_\vj,n)  \\
    % \norm[\cg]{S(f) - A(f,\varepsilon)} & \le \sum_{\vj \in \cn} \bigabs{\hf(\vj)} \norm[\cg]{v_\vj - \Sapp(u_{\vj},n)}
\end{align*}

\vspace{-7ex}
\alert{$\app(f,\varepsilon) = \Sapp(f,n) + $ stopping criterion}

@@

@@

\begin{frame}{Integration Using Function Values\footfullcite{DicEtal14a}}

@@

@@

\setlength{\figwidth}{0.3\textwidth}

@@

\begin{frame}{Solving General Linear Problems Using Series Coefficients\footfullcite{DinHic20a}}

@@

\begin{align*}
    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[2,\vlambda]{\hf} : = \norm[2]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
    \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[2]{\hg}\biggr \}, \qquad S(u_{\vj}) = v_{\vj} \\
      \lambda_{\vj_1} & \ge \lambda_{\vj_2} \ge \cdots, \qquad
      n_0 < n_1 < n_2 < \cdots,  \qquad
 	\sigma_k(f) = \sum_{i=n_{k-1}+1}^{n_k}  \bigabs{\hf(\vj_i)}, \quad k \in \naturals \\
     \cc &: = \left\{f \in \cf :  
 	 \sigma_\ell(f) \le a b^{\ell - k}\sigma_k(f) \quad \forall k \le \ell \right\} \quad a > 1 > b \quad \text{\alert{series coef.\ decay steadily}}\\
 	 \Sapp(f,n) &= \sum_{i=1}^n \hf(\vj_i) v_{\vj_i} \text{ is a optimal for fixed }n, \qquad \norm[\cg]{S(f) - \Sapp(f,n)} \le \frac{ab \sigma_k(f)}{\sqrt{1 - b^2}}
\end{align*}

>>>>

\vspace{-9ex}
\uncover<1->{\alert{Solvability}\footfullcite{KunEtal19a}: $\ca(\cc) \ne \emptyset$

@@

\uncover<2->{\alert{Cost}: $\cost(\app,f,\varepsilon) = $ \# of function data
\newline
 $\cost(\app,\cc,\varepsilon, \rho) = \max_{f \in \cc \cap \cb_{\rho}} \cost(\app,f,\varepsilon)$
 \newline
 $\cb_{\rho} := \{f \in \cf : \norm[\cf]{f} \le \rho \}$

@@

\uncover<3->{\alert{Tractability}\footfullcite{NovWoz08a}: $\comp(\app,\cc,\varepsilon, \rho) \le C \rho^p\varepsilon^{-p} d^{q} $}

@@

    %\item Union of \alert{cones} is a \alert{cone}

    \item Philosophy:  \alert{What we cannot observe is not much worse than what we can observe}

@@

\begin{frame}{Inputs and Outputs}

\vspace{-5ex}
\begin{gather*}
    \text{\alert{Input: }} f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} , \qquad 
    \text{\alert{Output: }} g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj}, \qquad S(u_{\vj}) = v_{\vj}, \\
    \text{E.g., Function recovery: } S(u_{\vj}) = u_{\vj} = v_{\vj}, \qquad
   \text{ Integration: } S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx  = v_\vj \\
    \text{\alert{Fixed sample size algorithm: }} \Sapp(f,n) = \sum_{i=1}^n L_i(f) g_i = \sum_{\vj \in \cn} \hf(\vj) \Sapp(u_\vj,n)  \\
    \alert{\app(f,\varepsilon) = \Sapp(f,n) + \text{ stopping criterion}}
\end{gather*}

@@

% \begin{frame}{Spaces of Inputs and Outputs}

% \vspace{-3ex}

% We focus on Banach spaces that look like

% \vspace{-5ex}
% \begin{align*}
%     \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[r,\vlambda]{\hf} : = \norm[r]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \quad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
%     \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[t]{\hg}\biggr \}, \qquad S(u_{\vj}) = v_{\vj}, \\
%     \text{E.g., } & \text{ Function recovery: } S(u_{\vj}) = u_{\vj} = v_{\vj} \\
%     & \text{ Integration: } S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx  = v_\vj\\
%     \Sapp(f,n) &= \sum_{i=1}^n L_i(f) g_i = \sum_{\vj \in \cn} \hf(\vj) \Sapp(u_\vj,n)  \\
%     % \norm[\cg]{S(f) - A(f,\varepsilon)} & \le \sum_{\vj \in \cn} \bigabs{\hf(\vj)} \norm[\cg]{v_\vj - \Sapp(u_{\vj},n)}
% \end{align*}

% \vspace{-7ex}
% \alert{$\app(f,\varepsilon) = \Sapp(f,n) + $ stopping criterion}

% \end{frame}

@@

\begin{frame}{Integration Using Function Values, $\LambdaStd$\footfullcite{DicEtal14a}}

@@

\vspace{-4ex}
\alert{Have } $\cost(f,A,\varepsilon)$; \quad \alert{No } $\cost(A,\cc,\varepsilon,\rho)$,  $\comp(\ca(\cc),\varepsilon,\rho)$, or  tractability results \alert{yet}

@@

\setlength{\figwidth}{0.4\textwidth}

@@

\begin{frame}{Solving General Linear Problems Using Series Coefficients, $\LambdaSer$\footfullcite{DinHic20a}}

@@

\begin{align*}
    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[2,\vlambda]{\hf} : = \norm[2]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
    \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[2]{\hg}\biggr \}, \qquad S(u_{\vj}) = v_{\vj} \\[-2ex]
      & \alert{\lambda_{\vj_1} \ge \lambda_{\vj_2} \ge \cdots}, \qquad
      n_0 < n_1 < n_2 < \cdots,  \qquad
 	\sigma_k(f) = \sum_{i=n_{k-1}+1}^{n_k}  \bigabs{\hf(\vj_i)}, \quad k \in \naturals \\
     \cc &: = \left\{f \in \cf :  
 	 \sigma_\ell(f) \le a b^{\ell - k}\sigma_k(f) \quad \forall k \le \ell \right\} \quad a > 1 > b \quad \text{\alert{series coef.\ decay steadily}}\\
 	 \Sapp(f,n) &= \sum_{i=1}^n \hf(\vj_i) v_{\vj_i} \text{ is a optimal for fixed }n, \qquad \norm[\cg]{S(f) - \Sapp(f,n)} \le \frac{ab \sigma_k(f)}{\sqrt{1 - b^2}} \\[-1ex]
 	 \alert{A(f,\varepsilon)} & \alert{= S(f,n_k) \text{ for the smallest $k$ satisfying } \sigma_k(f) \le \frac{\varepsilon \sqrt{1 - b^2}}{ab}}
\end{align*}
